---
title: "Group 20 CA pullution burden"
author: "Russell Fager, Hollie\tPennington"
date: "11/13/2021"
output: html_document
---

```{r setup, include=TRUE, message = FALSE, warning = FALSE}
knitr::opts_chunk$set(echo = TRUE, warning = FALSE, message = FALSE)

library(tidyverse)
library(janitor)
library(here)
library(hexbin)
```

```{r}
ces <- read_csv(here("data", "ces3demographics.csv")) %>% 
  clean_names()
```

```{r}
ggplot(data = ces, aes(x = white_percent, y = ces_3_0_score)) + 
  geom_hex() +
  labs (x = "% White Population", y = "CalEnviro Community Pollution Score",
        title = "% of CA White Population Living in Polluted Communites") + 
  scale_fill_gradient(low = "purple", high = "blue") + 
  theme_minimal()
```
**Figure 1. This density map shows the relationship between % white population and the aggregate CalEnviroScreen Community Pollution Score across >8,000 CA census tracts.**

The overall trend suggest that areas with a higher percentage of white people have a  lower environmental score. Areas with lower percentage of white people have a higher environmental score. This suggest that when the population has more white people, there is less pollution. 


CITATION: California Office of Environmental Health (2018). "CalEnviroScreen 3.0: A Tool For Advancing Environmental Justice," *California Environmental Protection Agency.* https://github.com/russellffager/ejscreen-group-20.git